Water desalination using polyelectrolyte hydrogel: Gibbs ensemble modeling

### 2022-09-02 MDPI/response_letter.tex

\item \textit{How do you think control factors in open system such as pressure and temperature}

\end{enumerate}

\textbf{Reviewer 2}
\textit{This manuscript is about creating a new model the thermodynamic equilibrium between coexisting phases of the gel and supernate aqueous solution.}
\begin{enumerate}

\item \textit{Abstract needs to re-write as and please follow the IMRAD instruction.}
\item \textit{There is introduction in the abstract, however, it needs to write more about the aim of this work, method, result and conclusion.}
\item \textit{Avoid to use word 'we' in the abstract as well as manuscript.}
Corrected.
\item \textit{line 247 in what table?}
\item \textit{Where is the method of this work?}
We did not want to bother the readers too much with technical aspects of the smulations. 
The method idea is outlined in the paragraph "Physics behind the desalination process" and described in the section "Theory behind the simulation". Some more technical issues are in ESI.
\item \textit{It is suggested that to carefully improve this manuscript as well as the writing and grammatical error.}
We improved the writing style of the manuscript and corrected the grammatical errors.
\item \textit{Please explain more detail about the process, how the process run and how the data could be explained and become more interesting for reader.}

@@

\end{enumerate}

\textbf{Reviewer 3}

\textit{}
\begin{enumerate}
\item \textit{The full stop in the title should be revised.}
Noted. Revised.
\item \textit{The abstract needs to be revised and be more attractive. The research gap, novelty and main findings should be concisely mentioned in the abstract.}
\item \textit{In this current shape, the manuscript looks like a report. The authors have to revise the flow of the context to attract the readers.}
We have revised and changed the manuscript to be more attractive for the readers. 
\item \textit{The manuscript must be improved by checking once again in English and technical writing. }
We improved the writing style of the manuscript and corrected the grammatical errors.

### 2022-09-02 gibbs.tex
Update gibbs.tex, MDPI/response_letter.tex

\subsection{Gibbs ensemble}
\todoi{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
TODO concise description of Gibbs ensemble

@@

@@

\paragraph{Compression in open system}
\begin{figure*}[t]
\subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub.pdf}}
\hspace{0.02\textwidth}
\subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub.pdf}}
\caption{
The compression of the gel in open system (solid lines) and in closed system (dotted lines). 
Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend). Shadowed area limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
\end{figure*}
First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
The simulations are run for a set of different simulation box volumes. 
Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.

@@

\begin{figure*}[t]
\subfloat[Pressure vs gel molar volume \label{fig: NV}]
{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub.pdf}}
\subfloat[Salinity vs gel molar volume\label{fig: CN}]
{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
\caption{The compression of the gel in \emph{open system} (solid lines) and in \emph{closed system} (dotted lines). 
Shadowed area limit the states with applied pressure below zero and above 5 bar.
The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.
\label{fig: NV and CN}}

>>>>

\subsection{Gibbs ensemble}
\todoi{We have the "Gibbs ensemble" in the title, and this term is not used in the manuscript at all.}
TODO concise description of Gibbs ensemble, solving the task to Reviewer 2, Q5 and Q7

@@

\subsection{Simulations}
TODO put here the parts from "Results and Discussion", which are actually neither Results nor Discussion
\paragraph{Compression in the \emph{open system}}
\paragraph{Compression in the \emph{closed system}}

@@

\paragraph{Compression in open system}
\begin{figure*}[t]
\subfloat[The gel partial pressure vs gel molar volume \label{fig: PV}]
{\includegraphics[width=0.48\textwidth]{figures/fig_PV_pub.pdf}}
\hspace{0.02\textwidth}
\subfloat[Supernate salinity vs gel molar volume\label{fig: CV}]
{\includegraphics[width=0.48\textwidth]{figures/fig_CV_pub.pdf}}
\caption{
The compression of the gel in the \emph{open system} (solid lines) and in the \emph{closed system} (dotted lines). 
Each solid curve corresponds to different salinity of the reservoir $\cs$ (see legend).
The shadowed areas limit the states with applied pressure below zero and above 5 bar.\label{fig: PV and CV}}
\end{figure*}
First, we run a set of simulations modeling the gel compression in \emph{open system}, \ie in equilibrium with a big bath of certain salinity, $\cs$. 
The simulations are run for a set of different simulation box volumes. 
Each simulation returns the averaged pressure, $P$, and the number of $\cl$ ions, which are present in the simulation box, $\ncl$.

@@

\begin{figure*}[t]
\subfloat[Pressure vs gel molar volume \label{fig: NV}]
{\includegraphics[width=0.49\textwidth]{figures/fig_NV_pub.pdf}}
\subfloat[Salinity vs gel molar volume\label{fig: CN}]
{\includegraphics[width=0.495\textwidth]{figures/fig_NVbox_mu_pub.pdf}}
\caption{The compression of the gel in the \emph{open system} (solid lines) and in the \emph{closed system} (dotted lines). 
The shadowed areas limit the states with applied pressure below zero and above 5 bar.
The values $N_\cl$ are the virtual numbers of present $\cl$ ions in \emph{closed system} simulation boxes.
\label{fig: NV and CN}}
